                %% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

%\usepackage{import}

% personal data
\name{Josh}{Marshall}
\address{11 Talcott Forest Road, Apt. G, Farmington, CT, 06032}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1 989 941 5787}                   % optional, remove / comment the line if not wanted
\email{joshua.r.marshall.1991@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{github.com/anadon}                         % optional, remove / comment the line if not wanted
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

% recipient data
\recipient{Human Resources}{MDI Biological Laboratory\\159 Old Bar Harbor Road\\Bar Harbor, ME, 04609}
\date{January 27, 2020}
\opening{To whom it may concern,}
\closing{Thank you for your time and consideration,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

%I was thinking about something more clearly establishing my programming and sys admin skill set, and performance last summer.

%Intent
I am seeking engaging work in an environment where computer science and biological research intersect.  I enjoy delving into systems that are large and complex; not only to further my understanding, but to optimize and improve such systems.  MDI's work presents fascinating questions and unique challenges with aging and other open questions through  epigenetics, transcriptomics, metabolism, genetics, and the proteome.


%Skillset
Through my education in Computer Science and Bioinformatics, I have strong foundational knowledge which helps me learn and apply new tools to complete objectives quickly and reliably.  I have established experience with \texttt{C}/\texttt{C++}, \texttt{Java}, \texttt{Python}, \texttt{SQL}, \texttt{Guile}, \texttt{Fortran}, \texttt{bash}, \texttt{matlab}, and more.  My current personal project is to develop a specification to use with \texttt{guix} and \texttt{gwl} in order to cache computations, create a sane metadata wrapped data file format, transparent HPC/cloud job submission, and serve as a general replacement to all global scale file distribution systems.  Regarding the preferred qualifications with \texttt{cwl} and \texttt{pandas}, I've used both in the past and am confident that I would be able to meet all of your technical needs.  I already have a general knowledge of biology, and would be excited to become more familiar with it through my technical contributions.


%Past work compatibility
My supervisors in prior positions have noted the quality, and reliability of code and are still supporting my efforts to advance professionally.  At Michigan Technological University, I held a University Senate Committee role on the Committee of Textbook Prices and started a textbook lending program.  At Arroyo Networks I wrote code which is still in use because of its clarity and elegance.  At Jackson Laboratory I've had a major role in several projects despite my brief time at the institution.  I encourage you to contact my references to hear others' appraisal of my attitude and skill.



\makeletterclosing

\end{document}


%% end of file `template.tex'.